\section{Expected Results and Timeline}
\label{sec:results}

This project will deliver practical tools and insights that advance predictable edge computing:

\begin{packeditemize}
    \item Network-agnostic time-budget estimation techniques that work across heterogeneous access networks without requiring RAN-specific coordination.
    \item Deadline-aware scheduling policies for edge CPU and GPU resources that improve SLO satisfaction under multi-tenant workloads.
    \item Overload control mechanisms that balance SLO satisfaction, fairness, and resource efficiency during periods of high contention.
    \item Open-source prototype implementation suitable for deployment on diverse edge platforms (ISP, CDN, MEC), including integration guidelines and performance evaluation tools.
    \item Comprehensive evaluation using traces from commercial edge deployments, demonstrating improved SLO satisfaction and reduced tail latency compared to existing approaches.
\end{packeditemize}

\mypara{Timeline (12 months):}
\begin{packeditemize}
    \item \textbf{Months 1--3:} Design and implement network-agnostic time-budget estimation techniques.
    Develop prototype edge runtime with basic deadline-aware scheduling.
    Validate time-budget estimation accuracy using collected traces from multiple access network types.
    \item \textbf{Months 4--6:} Extend edge runtime to support heterogeneous CPU and GPU workloads.
    Implement multi-tenant scheduling policies with deadline awareness.
    Conduct initial evaluation using synthetic workloads and edge application traces.
    \item \textbf{Months 7--9:} Design and implement overload control mechanisms including admission control and early-drop policies.
    Integrate all components into a cohesive prototype.
    Conduct comprehensive evaluation using realistic multi-tenant scenarios.
    \item \textbf{Months 10--12:} Refine prototype based on evaluation results.
    Prepare open-source release with documentation and deployment guidelines.
    Conduct final performance evaluation and prepare technical reports and publications.
\end{packeditemize}
