\section{Project Support and Resources}
\label{sec:support}

\subsection{Infrastructure and Testbed}

This research requires access to edge computing infrastructure and representative access network environments to develop and validate the proposed SLO-aware framework.
We will leverage our existing testbed infrastructure and seek collaboration opportunities for real-world deployment validation.

\mypara{Edge computing testbed:}
We have access to edge servers with CPU and GPU resources suitable for emulating ISP edge deployments.
These systems will host the prototype edge runtime and allow us to evaluate multi-tenant scenarios with realistic workload mixes.

\mypara{Access network diversity:}
To validate network-agnostic time-budget estimation, we require access to traces or testbed environments representing diverse access technologies including cable, Wi-Fi, cellular, and wired connections.
We will work with Comcast and leverage publicly available datasets where appropriate to ensure the framework generalizes across network types.

\subsection{Collaboration and Deployment Opportunities}

We are interested in collaborating with Comcast to:
\begin{packeditemize}
\item Obtain representative workload traces and network characteristics from production edge deployments.
\item Validate the prototype framework in realistic ISP edge environments.
\item Identify deployment constraints and integration requirements for production systems.
\item Explore opportunities for technology transfer and open-source contributions.
\end{packeditemize}
